---
title: "Prediction Assignment Writeup"
author: "Yuan Wei"
date: "November 21, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required Packages
```{r package, warning=FALSE, message=FALSE}
library(caret)
library(dplyr)
library(ggplot2)
```


## Reading Raw Data
```{r file, warning=FALSE, message=FALSE}
train <- read.csv("pmltraining.csv", header = TRUE, na.strings = c("", "NA"))
test <- read.csv("pmltesting.csv", header = TRUE, na.strings = c("", "NA"))
  
```

## Data cleaning
Remove all column with less than half of the information, and timestamp.
```{r clean}
train.keep <- c((colSums(!is.na(train[,-ncol(train)])) >= 0.6*nrow(train)))
test.keep <- c((colSums(!is.na(test[,-ncol(test)])) >= 0.6*nrow(test)))
train.clean <- train[, train.keep]
test.clean <- test[, test.keep]
train.clean <- train.clean[, -(1:2)]
test.clean <- test.clean[, -(1:2)]
```


## Model fitting
Separate 60% of the training data set as training and the remaining for validation. Once the best model is found, it will be validated on the original testing data set
```{r train, cache=TRUE}
inTrain <- createDataPartition(train.clean$classe, p = 0.6, list = FALSE)
train.set <- train.clean[inTrain, ]
vad.set <- train.clean[-inTrain, ]
```

## Model prediction with Random Forest
Using all variable to create a random forest model.
```{r validating, warning=FALSE, message=FALSE}
mod1 <- train(classe ~ ., method = "rf", data = train.set)
pred.rf <- predict(mod1,vad.set)
cm <- confusionMatrix(pred.rf, vad.set$classe)
cm
```


## Final Prediction
Using random forest model on test data set.
```{r predict}
finalPred <- predict(mod1, test.clean)
finalPred
```
